Investigating PCA image reconstruction for pedestrian detection

### 2010-05-04 paper/paper.tex
Alteração na introdução.

In this paper we describe a pedestrian detection proposed by Malangon-Borja \cite{borja09}. It classifies an image based on how much its reconstruction is different from the original one, that is, it classifies based on the image reconstruction error. We analyze how it works and how its original performance can be improved, as well as its detection times, by using weights on the reconstruction errors and reducing the number of calculations made by the algorithm, respectively.

>>>>

In this paper we describe a pedestrian detection proposed by Malangon-Borja \cite{borja09}. It classifies an image based on how much its reconstruction is different from the original one, that is, it classifies based on the image reconstruction error. We analyze how it works and how its original performance can be improved.

The proposed improvements enhances the system's accuracy using weights on the detection errors and significantly reduces execution times by decreasing the number of calculations made by the algorithm.

% and, by using weights on the reconstruction errors, we improve the system's accuracy.
